CGAT In The Hat

### 2012-12-06 paper/paper.tex
In the process of expanding the introduction of the paper.

\section{Introduction}\label{sec:introduction}
Gene annotation is the process of associating metadata about a gene with the
contig, a dna sequence, on which the gene resides.\cite{annotation} This metadata is necessary for conducting
genomic research projects and analysis involving the contig's genomic sequence.
Currently, there is no specialty gene annotation software. Genome browsers
all maintain lots of genomic data and are used when manually annotating genes,
but do not provide a user-friendly interface. While genome browsers
will likely never be replaced (UCSC genome browser, etc. are well
established\cite{ucscbrowser, ncbi}), it would be desirable to have a software system that better
accommodates the visual and informational needs of gene annotation.

@@

\paragraph{GET Requests}
\begin{itemize}
\item administration\_info - Provides the user with meta information information that the user would need to perform administrative tasks such as creating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user\_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign\_task - Ask a group of people to perform an annotation.
\item cancel\_notification - Clear a notification from a user.
\item create\_annotation - Create a new annotation of a contig.
\item create\_group - Create a group.
\item join\_group - Join a group.
\item leave\_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse\_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save\_annotation - Save a work-in-progress annotation.
\item set\_help - Upload a help page.
\item submit\_annotation - Submit a finalized annotation.
\item upload\_contig - Upload a contig into CGAT.
\end{itemize}

>>>>

\section{Introduction}\label{sec:introduction}
Genomics research attempts to understand information maintained in the genomes
of various organisms. A \textit{genome} is a sequence of DNA containing all
information for an organism. Genomes contain several types of regions,
\textit{exons}, \textit{introns}, \textit{CDS}s,   In order to link biological information of the organism
to genomic information in the DNA sequence... to  To understand this information, it
\cite{annotation}

Gene annotation is the process of associating metadata about a gene with the
contig, a dna sequence, on which the gene resides.\cite{annotation} This metadata is necessary for conducting
genomic research projects and analysis involving the contig's genomic sequence.
Currently, there is no specialty gene annotation software. Genome browsers
all maintain lots of genomic data and are used when manually annotating genes,
but do not provide a user-friendly interface. While genome browsers
will likely never be replaced (UCSC genome browser, etc. are well
established\cite{ucscbrowser, ncbi}), it would be desirable to have a software system that better
accommodates the visual and informational needs of gene annotation.

@@

\paragraph{GET Requests}
\begin{itemize}
\item administration_info - Provides the user with meta information information that the user would need to perform administrative tasks such as creating a group or assigning a task.
\item annotation - Provide the user with information about an specified annotation.
\item contig - Get information about a specific contig.
\item gene - Get information about a specific gene.
\item group - Get information about a specific group.
\item help - Get help information on a specific topic.
\item user_profile - Get the profile information about a specific user. If the user is logged in and requests information about themselves, more information is provided.
\end{itemize}

@@

\begin{itemize}
\item assign_task - Ask a group of people to perform an annotation.
\item cancel_notification - Clear a notification from a user.
\item create_annotation - Create a new annotation of a contig.
\item create_group - Create a group.
\item join_group - Join a group.
\item leave_group - Leave a group.
\item login - Login.
\item logout - Logout.
\item parse_fasta - Upload a FASTA file to the server, parse the contents, and returned the parsed structure.
\item register - Register a new user.
\item save_annotation - Save a work-in-progress annotation.
\item set_help - Upload a help page.
\item submit_annotation - Submit a finalized annotation.
\item upload_contig - Upload a contig into CGAT.
\end{itemize}
